Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-03-16 paper/paper.tex
tmp -> paper

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{grffile}

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
    compressed with VD only.
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\linewidth]{../assets/grad_log.pdf}
  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
  \label{fig:molchanov-derivative-replica}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__fashionmnist}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__mnist}
\end{figure}

>>>>

\usepackage{xcolor}
\usepackage{graphicx, url}
\usepackage{grffile}

\graphicspath{{../assets/}}

@@

\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
  \end{subfigure}
  \caption{%
    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
  }
  \label{fig:hist__and__threshold__tradeoff}
\end{figure}

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!t]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
    compressed with VD only.
  }
  \label{fig:musicnet__trade-off}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\columnwidth]{grad_log.pdf}
  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
  \label{fig:molchanov-derivative-replica}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__fashionmnist}
\end{figure}

\begin{figure}[!h]
  \centering
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off on the letters part of the MNIST dataset.
    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
  }
  \label{fig:mnist-like__trade-off__mnist}
\end{figure}
